\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{\Large Bhanuteja Aryasomayajula} % Your name
%\address{5B/137, Sai Sri Grandway Enclave, Chowdariguda, Hyderabad - 500088} 
\address{(+91)8927872353 \\ teja275@gmail.com \\ https://www.linkedin.com/in/tejaaryan/}
\usepackage[official]{eurosym}
\begin{document}

\begin{rSection}{Summary}
A passionate Data Scientist with the right mix of technical skills and business acumen having 5 years of experience in building data driven solutions spanning IoT, Manufacturing, Supply Chain, Health Care \& Financial Services domains.
\end{rSection}

\begin{rSection}{Education}

{\bf Indian Institute of Technology, Kharagpur} \hfill {\em June 2011 - June 2016} 
\\ B.Tech. (Hons.) \& M.Tech. in Mechanical Engineering.\hfill { Overall CGPA: 7.39/10}

\end{rSection}



\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l}
Languages \ & Python, SAS, MATLAB\\
Databases & MySQL, SQLite, Hive\\
Cloud Technologies & AWS, Google Cloud\\
Version Control & GitHub\\
Techniques & Tree based models, Nearest Neighbors, Clustering, Gaussian Processes, \\ & Time Series Forecasting, Neural Networks, Hidden Markov Models\\ 
\end{tabular}
%\begin{table}[htbp]
%    \begin{tabular}{lp{35em}}
%    \textbf{Languages} & \multicolumn{1}{l}{Python, SAS, MATLAB} \\
%    \textbf{Databases} & \multicolumn{1}{l}{MySQL, SQLite, Hive} \\
%    \textbf{Cloud Techologies} & \multicolumn{1}{l}{AWS, Google Cloud} \\
%    \textbf{Version Control} & \multicolumn{1}{l}{GitHub} \\
%    \textbf{Techniques} & Regressions, Tree based models, Nearest Neighbours, Clustering, Gaussian Processes, Time Series Forecasting, Neural Networks, CNNs \\
%    \end{tabular}%
%  \label{tab:addlabel}%
%\end{table}%


\end{rSection}
% 
% 
% \newpage
\begin{rSection}{Work Experience}
\begin{rSubsection}{\large Bosch Center for Artificial Intelligence, Bengaluru}{\textbf{\large Aug 2019 - present}}{\large Senior Data Scientist}{}

 \item Part of the global team at Bosch responsible for incorporating Artificial Intelligence into Bosch products and processes.\\\\
%{\bf Automated Commissioned Air Leakage Detection}
{\textbf{\textit{Automated Air Leakage Detection}}}
 \item Built and deployed a \textbf{Random Forest} based automated air leakage detection algorithm for the manufacturing plants at BSH Hausgeräte GmbH.
 \item Worked with ultra sound data and engineered features using techniques like \textbf{Fourier Transforms, Power Spectral Density, Kurtosis, Skewness} etc. which resulted in a model accuracy of \textbf{99.2\%}.
 \item The fully developed solution (hardware \& software) has an estimated target market of \textbf{180 Mn \euro{}}.\\\\
%{\bf Vivalytic - Automated Spot Detection Algorithm}
{\textbf{\textit{Vivalytic - Automated Spot Detection Algorithm}}}
 \item Vivalytic is a universal platform for molecular diagnostics that can analyze sample materials in a fully automated way via designated cartridges, the result being indicated in the form of fluorescent spots.
 \item Built a \textbf{CNN} based spot detection algorithm which has been deployed in the Vivalytic platform.
 \item Experimented with various techniques like \textbf{Dynamic Drop-out \& Cross Validation} to improve the model performance and robustness, achieved an overall accuracy of \textbf{99.77\%}.
 \item Forecasted sales revenue of the platform by 2025 is more than \textbf{250 Mn \euro{}}.\\\\
{\textbf{\textit{Machinery Spare Part Inventory Optimization}}}
 \item Developed and deployed a fully automated solution for spare part stock inventory planning in manufacturing plants of Bosch's Power Train Solutions division.
  \item Employed \textbf{probabilistic techniques} like \textbf{reorder point } and \textbf{economic order quantity} models, thereby ensuring timely availability of spare parts and avoiding production shut downs.
  \item Built and integrated an \textbf{outlier detection} engine into the above solution which generates alerts for parts having anomalous consumption patterns.
 \item The solution has been deployed for usage in \textbf{16 manufacturing plants across Europe} accounting for an annual inventory savings of \textbf{3 Mn \euro{}}.\\\\
%{\bf Electric Car Battery Aging Prediction}
{\textbf{\textit{Electric Car Battery Aging Prediction}}}
 \item Built a \textbf{Gaussian Process} based model to improve the robustness and accuracy of the state of health estimation of EV batteries. 
 \item Worked with battery aging data containing electro-chemical parameters, temperature, voltage, charging \& discharge current related information. Employed multiple data augmentation techniques like \textbf{Jittering, Warping, Pattern Mixing} etc. to handle data scarcity.
 \item Forecasted sales revenue of the platform by 2025 is \textbf{104 Mn \euro{}} with the AI solution contributing \textbf{1\%}.\\\\
{\textbf{\textit{Miscellaneous}}}
 \item Represented Bosch at the \textbf{campus recruitment} events of multiple top-tier Indian universities to setup a best-in-class Artificial Intelligence team for Bosch in India.
 \item Conceptualized and implemented a company wide initiative "\textbf{Prod-casts}" in order to improve the awareness of Artificial Intelligence among Boschlers.\\
 \noindent\rule{6.75in}{0.1pt}
\end{rSubsection}

\begin{rSubsection}{\large American Express India Pvt. Ltd., Gurugram}{\textbf{\large Aug 2016 - Aug 2019}}{\large Data Scientist}{}
 \item Part of the credit limit management team responsible for consulting 14 proprietary markets of American Express' lending business outside the US with an annual billed business of over 7Bn \$ (as on Aug 2019).\\\\
{\textbf{\textit{Risk \& Credit Limit Strategy Development}}}
 \item Used predictive analytics to determine consumer's behavior and thereby assign the right credit limit to mitigate risk exposure.
 \item Responsible for architecture, implementation and delivery of an enhanced \textbf{kNN model} based credit limit assignment strategy for new credit card applications in Australia \& the UK.
 \item Closely worked with business partners spanning across strategy, marketing and technology to drive initiatives with a revenue impact of \textbf{20Mn \$} in a span of 2 years.\\\\
{\textbf{\textit{Mentorship \& Training}}}
 \item \textbf{Mentored 2 new hires} by taking knowledge transfer sessions and been a subject matter expert of the credit limit function across the company's global risk center of excellence.
  \item Consistently received \textbf{highest year end ratings and awards from top level management} for excellent performance, driving results and exhibiting leadership behavior.
\end{rSubsection}

\end{rSection}
% 
\begin{rSection}{Academic Achievements} 
\item Secured All India Ranks 982(top 0.2\%) in IIT JEE - 2011 and 875(top 0.07 \%) in AIEEE - 2011.
\item Finalist in Indian National Physics \& Astronomical Olympiads in 2010.
\item Winner of under 15 district level Sudoku championship held by Rotary Club, Visakhapatnam.
\end{rSection}

\begin{rSection}{Extra-Curricular} 
\item Successfully led a 100+ member dramatics club in university to put up stage plays witnessed by 800+ strong audience.
\item Cadet at No. 3 Bengal Technical (Air) Squadron National Cadet Corps. Trained at using a .22 Long Rifle.
\end{rSection}

\end{document}
